---
title: "Temperature and Seoul Bike"
output: pdf_document
---
Aim: 

* To demonstrate how to do a machine learning in R for beginners (no prerequisite knowledge)

* To use a linear regression model to predict Seoul bike rent demand from temperature

* Only necessary codes are included and codes such as making plot neat are excluded

Code written by: Ggodburi AI (Youtuber)

* URL for the youtube: https://www.youtube.com/channel/UCUdyx4YZ_bkBmBS3aq_7Xag

Data set source: 

* Sathishkumar V E, Jangwoo Park, and Yongyun Cho. 'Using data mining techniques for bike sharing demand prediction in metropolitan city.' Computer Communications, Vol.153, pp.353-366, March, 2020

* Sathishkumar V E and Yongyun Cho. 'A rule-based model for Seoul Bike sharing demand prediction using weather data' European Journal of Remote Sensing, pp. 1-18, Feb, 2020

* Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.

* URL: https://archive.ics.uci.edu/ml/datasets/Seoul+Bike+Sharing+Demand


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data 

```{r}
# Before loading data, the two column names need to be changed for the encoding issue.
# Temperature(?C) -> Temperature
# Dew point temperature(?C) -> Dew point temperature

data_frame = read.csv('SeoulBikeData.csv')
summary(data_frame)
```

```{r}
head(data_frame)
```


## Scatter plot between Temperature and Rented bike count 
```{r}
plot(x=data_frame$Temperature ,y=data_frame$Rented.Bike.Count)
```

## Modeling by using linear regression (a basic form of machine learning)
```{r}
# y(bike rent count) = a (parameter) * x (temperature) + b (parameter)
# by using regression, we can derive parameters a and b which represent the data best 
# (minimizing the errors)

# formula argument format = Y ~ X
linear_regression_model = glm(formula = Rented.Bike.Count ~ Temperature, data=data_frame) 
summary(linear_regression_model)
```

## Predict the bike rent count by using the derived $a$ and $b$ for any temperature 

```{r}
temp_temperature = 23
a = 29.0811
b = 329.9525

y = a * temp_temperature + b
y
```

```{r}
predict(linear_regression_model, newdata=data.frame(Temperature=c(23)))
```
## Plot the best fit line in red using the derived parameters  
```{r}
plot(x=data_frame$Temperature ,y=data_frame$Rented.Bike.Count)
abline(a=b,b=a, col='red')
```

## Show several predicted bike counts according to given temperatures
```{r}
temperature_list = c(-10,0,10,20,30,40)
pred_list = predict(linear_regression_model, newdata=data.frame(Temperature=temperature_list))

data.frame(Temperature=temperature_list, Pred_bike_count=pred_list)
                                                
```






